cardinalR: Generating interesting high-dimensional data structures

### 2025-08-21 paper-cardinalR.Rmd
Add the table for multicluster data generation

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_multigrid",
                                "make_threeclust01",
                                "make_fourclust01",
                                "make_fiveclust01"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                "",
                                ""))
```

>>>>

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_klink_circles",
                                "make_chain_circles",
                                "make_klink_curvycycle",
                                "make_chain_curvycycle",
                                "make_gaucircles",
                                "make_gaucurvycycle",
                                "make_onegrid",
                                "make_twogrid_overlap",
                                "make_twogrid_shift",
                                "make_shape_para",
                                "make_three_clust_"), 
                        exp = c(
    "Generates a Möbius-like cluster combined with a Gaussian cluster.",
    "Generates multiple Gaussian clusters in high-dimensional space.",
    "Generates a curvilinear cluster with a Gaussian cluster.",
    "Generates K-link circular clusters (non-linear circular patterns).",
    "Generates chain-like circular clusters connected sequentially.",
    "Generates K-link curvy cycle clusters (curvilinear loop structures).",
    "Generates chain-like curvy cycle clusters connected sequentially.",
    "Generates circular clusters with a Gaussian cluster in the middle.",
    "Generates curvy circular clusters with a Gaussian cluster in the middle.",
    "Generates a single grid in two dimensions.",
    "Generates two overlapping grids.",
    "Generates two grids shifted relative to each other.",
    "Generates parallel shaped clusters.",
    "Generates three clusters with different shapes. (eg:- 01, 02, ..., 20)"))
```

### 2025-08-21 paper-cardinalR.tex
Add the table for multicluster data generation

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & \\
make\_multigau & \\
make\_curvygau & \\
make\_multigrid & \\
make\_threeclust01 & \\
\addlinespace
make\_fourclust01 & \\
make\_fiveclust01 & \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & Generates a Möbius-like cluster combined with a Gaussian cluster.\\
make\_multigau & Generates multiple Gaussian clusters in high-dimensional space.\\
make\_curvygau & Generates a curvilinear cluster with a Gaussian cluster.\\
make\_klink\_circles & Generates K-link circular clusters (non-linear circular patterns).\\
make\_chain\_circles & Generates chain-like circular clusters connected sequentially.\\
\addlinespace
make\_klink\_curvycycle & Generates K-link curvy cycle clusters (curvilinear loop structures).\\
make\_chain\_curvycycle & Generates chain-like curvy cycle clusters connected sequentially.\\
make\_gaucircles & Generates circular clusters with a Gaussian cluster in the middle.\\
make\_gaucurvycycle & Generates curvy circular clusters with a Gaussian cluster in the middle.\\
make\_onegrid & Generates a single grid in two dimensions.\\
\addlinespace
make\_twogrid\_overlap & Generates two overlapping grids.\\
make\_twogrid\_shift & Generates two grids shifted relative to each other.\\
make\_shape\_para & Generates parallel shaped clusters.\\
make\_three\_clust\_ & Generates three clusters with different shapes. (eg:- 01, 02, ..., 20)\\
\bottomrule
\end{tabular}
\end{table}
